**Defining protein biomarkers for *Candida albicans* extracellular vesicles**

### 2019-01-22 manuscript/README.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

# candidaev

This repository contains the data and code for our paper:

> Authors, (YYYY). _Title of paper_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Title of paper'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/csdaw/candidaev/archive/master.zip>

Or you can install this compendium as an R package, candidaev, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("csdaw/candidaev")
```
### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

# manuscript

This directory contains the final manuscript as submitted to Molecular
and Cellular Proteomics. It also contains templates and other files necessary 
for producing the `manuscript.pdf` file from the associated `manuscript.Rmd`.

# contents
```
    .
    ├── ...
    ├── /manuscript
    │    ├── /figures            # Contains figures draw by hand
    │    ├── /templates          # Contains citation and pagebreak templates
    │    ├── manuscript.Rmd      # R markdown file to produce manuscript.pdf
    │    ├── manuscript.pdf      # Final submitted manuscript
    │    ├── references.bib      # BibTex file containing manuscript references
    │    ├── README.Rmd          # R markdown file to produce README.md
    │    └── README.md           # Description of /manuscripts directory
    └── ...

```

### 2019-01-22 manuscript/manuscript.Rmd
Update each README.md
Update each README.md to describe contents of each directory.

Remove CONDUcT.md and CONTRIBUTION.md.

Add the following:
 - mcp.csl file for correct citation style.

 - pagebreak.lua, a filter to convert LaTeX \newpage command into
   appropriate markup for other formats e.g. html, docx. See:
   https://github.com/pandoc/lua-filters/tree/master/pagebreak

---
title: "Title Goes Here"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv(here::here('analysis', 'data', 'raw_data', 'my_csv_file.csv'))
```

@@

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

@@

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
git2r::repository(here::here())
```

>>>>

---
title: "**Defining protein biomarkers for *Candida albicans* extracellular vesicles**"
author: "*Charlotte Dawson^a^, Mark Bleackley^a^, Marilyn Anderson^a^*"
date: "*^a^Department of Biochemistry and Genetics, La Trobe University, Victoria, Australia*"
output: 
    bookdown::word_document2:
      pandoc_args:
        '--lua-filter=templates/pagebreak.lua'
      reference_docx: "templates/draft_template.docx"
      fig_caption: yes
    html_notebook: default
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: references.bib
csl: "templates/molecular-and-cellular-proteomics.csl"
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
---

**Running title:** Running title goes here

**Corresponding author:**

\newpage

@@

# Abbreviations

EV - extracellular vesicle

\newpage

# Abstract

The abstract goes here.

\newpage

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv(here::here('analysis')
```

@@

@@
